---
title: "assignment B4"
author: "Xin Wang"
date: "2023-11-14"
output: github_document
Roxygen: list(markdown = TRUE)
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Exercise 1 (37.5 points)
Take a Jane Austen book contained in the _janeaustenr_ package, or another book from some other source, such as one of the many freely available books from Project Gutenberg (be sure to indicate where you got the book from). Make a plot of the most common words in the book, removing “stop words” of your choosing (words like “the”, “a”, etc.) or stopwords from a pre-defined source, like the stopwords package or _tidytext::stop_words_.

If you use any resources for helping you remove stopwords, or some other resource besides the janeaustenr R package for accessing your book, please indicate the source. We aren’t requiring any formal citation styles, just make sure you name the source and link to it.

```{r}
# Install and load required packages
if (!requireNamespace("janeaustenr", quietly = TRUE)) {
  install.packages("janeaustenr")
}

if (!requireNamespace("tidytext", quietly = TRUE)) {
  install.packages("tidytext")
}

if (!requireNamespace("ggplot2", quietly = TRUE)) {
  install.packages("ggplot2")
}

if (!requireNamespace("dplyr", quietly = TRUE)) {
  install.packages("dplyr")
}

# Load required libraries
library(janeaustenr)
library(tidytext)
library(ggplot2)
library(dplyr)
```

Steps:

```{r}
# Load the Jane Austen book from janeaustenr package
emma_text <- janeaustenr::austen_books() %>%
  filter(book == "Emma") %>%
  select(text)

# Tokenize the text
emma_words <- emma_text %>%
  unnest_tokens(word, text)

# Get stop words from tidytext package
stop_words <- tidytext::stop_words

# Remove stop words
emma_words <- anti_join(emma_words, stop_words, by = "word")

# Get the most common words
common_words <- emma_words %>%
  group_by(word) %>%
  summarize(n = n()) %>%
  top_n(10, n)

# Plot the most common words
ggplot(common_words, aes(x = reorder(word, -n), y = n)) +
  geom_col() +
  labs(title = "Top 10 Most Common Words in Jane Austen's Emma (excluding stop words)",
       x = "Word",
       y = "Frequency")
```

# Exercise 2 (37.5 points)
Make a function that converts words to your own version of Pig Latin.

The specific input and output that you decide upon is up to you. Don’t forget to implement good function-making hygiene: we’ll be looking for (unrendered) roxygen2-style documentation (being sure to describe your Pig Latin conversion), examples of applying the function, 3 non-redundant tests, appropriate use of arguments, and appropriate amount of checking for proper input.

Your Pig Latin should incorporate two components:

## Rearrangement component

The default Pig Latin rearrangement rule, as per Wikipedia, moves beginning letters to the end:

1. For words that begin with consonant sounds, all letters before the initial vowel are placed at the end of the word sequence.
2. When words begin with consonant clusters (multiple consonants that form one sound), the whole sound is added to the end.
3. For words beginning with vowel sounds, one removes the initial vowel(s) along with the first consonant or consonant cluster.

Modify this somehow. Maybe you move letters from the end to the beginning, or you change the rules altogether, keeping a similar level of complexity.

## Addition component

The default Pig Latin addition rule is to add “ay” to the end of the word, after rearranging the letters of the word. You should choose some other addition rule.

```{r}
#' Convert words to a custom Pig Latin
#'
#' This function converts words to a custom Pig Latin by rearranging letters and adding a custom ending.
#'
#' @param words A character vector of words to be converted to Pig Latin.
#'
#' @return A character vector containing the words converted to Pig Latin.
#'
#' @examples
#' pig_latin(c("what", "your", "name"))
#' # Output: [1] "atwhoi" "ouryoi" "amenoi"
#' 
#' pig_latin(c("university", "british", "columbia"))
#' # Output: [1] "iversityunoi" "itishbroi"    "olumbiacoi"  
#'
#' @export
pig_latin <- function(words) {
  if (!is.character(words)) {
    stop("Input must be a character vector.")
  }

  pig_latin_word <- function(word) {
    # Rearrangement component
    vowels <- c("a", "e", "i", "o", "u")
    if (substr(word, 1, 1) %in% vowels) {
      # For words beginning with vowel sounds
      pig_word <- paste0(substr(word, 2, nchar(word)), substr(word, 1, 1))
    }  else {
      pig_word <- word
    }
      
    # For words that begin with consonant sounds or consonant cluster
    pig_word <- gsub("^([^aeiou]+)([aeiou].*)", "\\2\\1", pig_word, ignore.case = TRUE)

    # Addition component 'oi'to the end of the word, after rearranging the letters of the word.
    pig_word <- paste0(pig_word, "oi")

    return(pig_word)
  }
  return(as.character(sapply(words, pig_latin_word)))
}

```


```{r}
pig_latin(c("what", "your", "name"))
pig_latin(c("university", "british", "columbia"))
```


The test results

```{r}
if (!requireNamespace("testthat", quietly = TRUE)) {
  install.packages("testthat")
}

library(testthat)

test_that("Pig Latin conversion works correctly", {
  # Test 1: Basic test
  expect_equal(pig_latin(c("hello", "world", "apple")), c("ellohoi", "orldwoi", "eapploi"))

  # Test 2: Test with words starting with consonant clusters
  expect_equal(pig_latin(c("glove", "queen", "school")), c("ovegloi", "ueenqoi", "oolschoi"))

  # Test 3: Test with words starting with vowels
  expect_equal(pig_latin(c("elephant", "igloo", "umbrella")), c("ephanteloi", "ooigloi", "ellaumbroi"))
})
```

